### 2017-11-04 monograph/thesis/chapters/good_practices.tex
Remodeled the introduction.tex goals section and removed invalid
informations.
Removed copied text on good_practices.tex and let only the
reference to the original text.

    \begin{itemize}

    \item Global identifiers must start with `g\_' prefix.

    \item Global identifiers which are constant must be written in ALLCAPS.

    \item Boolean variables must be prefix with `is\_' even when they are in
    global scope, meaning double prefixed as `g\_is\_'.

    \end{itemize}

@@

    \subsection{?. Notation}

@@

>>>>

    \begin{itemize}
        \item Global identifiers must start with `g\_' prefix.
        \item Global identifiers which are constant must be written in ALLCAPS.
        \item Boolean variables must be prefix with `is\_' even when they are in
        global scope, meaning double prefixed as `g\_is\_'.
    \end{itemize}

@@

    \subsection{Other Notations}

@@

    \subsection{Spaces and Tabs}

    Either use spaces, or tabs
    \footnote{\url{https://blog.codinghorror.com/whitespace-the-silent-killer/}}.
    However while using tabs,
    you may end up with mixed file with tabs and spaces \cite{tabsAndSpacesConversion}.

    \section{Continuous Integration}

    On a distributed version control system,
    continuous integration would be continuously running the system tests
    as long new code is integrated into main system
    from the distributed clients \cite{continuousIntegration}.

    \subsection{Test Driven Development}

    \footnote{\url{https://blog.codinghorror.com/check-in-early-check-in-often/}}

    \cite{aspectOriented}
